MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-14 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
save to test folder on Synapse

devtools::install_github("GabrielHoffman/mvBIC")
library(mvBIC)

@@

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21867938'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL

@@

<!-- # Code -->
<!-- CODE <- Folder(name = "test mvBIC - MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN", parentId = parentId) -->
<!-- CODE <- synStore(CODE) -->

<!-- # Store covariates -->
<!-- COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID') -->
<!-- write.table(COVARIATES, file = 'CMC_ACC_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F) -->
<!-- COV_OBJ = synapser::File('CMC_ACC_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id) -->
<!-- COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName,  -->
<!--                       executed = thisFile, activityDescription = activityDescription) -->
<!-- synSetAnnotations(COV_OBJ, annotations = all.annotations) -->

>>>>

library(mvBIC) # devtools::install_github("GabrielHoffman/mvBIC")

@@

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='test-mvBIC')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21867938'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL

@@

# Code
``` {r save_code}
CODE <- Folder(name = "test mvBIC - MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN", parentId = parentId)
CODE <- synStore(CODE)
```
<!-- # Store covariates -->
<!-- COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID') -->
<!-- write.table(COVARIATES, file = 'CMC_ACC_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F) -->
<!-- COV_OBJ = synapser::File('CMC_ACC_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id) -->
<!-- COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName,  -->
<!--                       executed = thisFile, activityDescription = activityDescription) -->
<!-- synSetAnnotations(COV_OBJ, annotations = all.annotations) -->
